Uniform sampling without any cells to count trees

### 2024-07-08 No_tree_no_grid.Rmd
Mardi midi
No excluded tree

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

@@

```{r}
# Sample size
n <- 100
```

@@

```{r}
# Estimated value
est_ind <- sum((random_points$rho2)/p)
# 510000 e.g.
```

@@

```{r}
# Estimated value
est_x <- sum((random_points$x)/p)
# 499690876 e.g.
```

@@

```{r}
var_area <- ((1000*1000)/(n-1))*est_carre - (1/(n-1))*(est_area^2)
# The empirical variance is null as expected
```

@@

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_area, "\nVariance empirique :", var_area)
```

@@

```{r}
var_ind <- ((1000*1000)/(n-1))*est_ind - (1/(n-1))*(est_ind^2)
# Empirical variance: 2.491e+09 e.g.
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_ind <- half_area/p - (1/n)*(half_area^2)
# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
# Close to the empirical one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_ind, "\nVariance empirique :", var_ind)
```

@@

```{r}
var_x <- ((1000*1000)/(n-1))*est_x2 - (1/(n-1))*(est_x^2)
# Empirical variance: 8.407871e+14 ?!
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
# Close to the empirical one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_x, "\nVariance empirique :", var_x)
```

@@

```{r}
rm(a1, a2, x, y, b, col_, col_names) # Useless now
```

@@

```{r}
# Empirical mean based on MC
cat("Total à estimer :", val_x, "\nMoyenne des estimations obtenues :", mean(est_MC)) 
# should be close to 5e+08
# 499121662 e.g.
```

```{r}
# Empirical standard deviation based on MC
cat("Variance associée aux échantillons de Monte Carlo :", sd(est_MC))
# 28710306 e.g.
```

@@

  # 2nd step: creating the values corresponding to the function
  rho_MC <- tibble(.rows = n)
    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
    colnames(rho_MC) <- col_names
  }
  # rho_MC$x.1 <- NULL
  # rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

@@

  est_value <- mean(est_MC) # Estimated value
  return(est_value)
}
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
cat("True integral:", 1e+06, "\nMean of all the estimations:", res)
# 1e+06 1e+06 (Equality as always)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
cat("True integral:", 500000, "\nMean of all the estimations:", res)

# Ex:
# True integral: 5e+05
# Mean of all the estimations: 499600
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
cat("True integral:", 5e+08, "\nMean of all the estimations:", res)

# Ex:
# True integral: 5e+08
# Mean of all the estimations: 500189987
```

>>>>

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column and tibble
```

@@

```{r}
# Sample size
n <- 1000
```

@@

```{r}
# Estimated value
est_ind <- sum((random_points$rho2)/p)
# 492000 e.g.
```

@@

```{r}
# Estimated value
est_x <- sum((random_points$x)/p)
# 490781983 e.g.
```

@@

```{r}
var_area <- ((1000*1000)/(n-1))*est_carre - (1/(n-1))*(est_area^2)
# The variance estimation is null as expected
```

@@

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_area, "\nEstimation de la variance :", var_area)
```

@@

```{r}
var_ind <- ((1000*1000)/(n-1))*est_ind - (1/(n-1))*(est_ind^2)
# Variance estimation: 250186186 e.g.
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_ind <- half_area/p - (1/n)*(half_area^2)
# Theoretical variance: 2.5e+08, i.e. around 250186186
# Close to the empirical one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_ind, "\nEstimation de la variance :", var_ind)
```

@@

```{r}
var_x <- ((1000*1000)/(n-1))*est_x2 - (1/(n-1))*(est_x^2)
# Variance estimation: 8.341029e+13
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
# Theoretical variance: 8.333333e+13, i.e. around 8.341029e+13
# Close to the estimated one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_x, "\nEstimation de la variance :", var_x)
```

@@

```{r}
rm(a1, a2, x, y, b, col_names) # Useless now
```

@@

```{r}
# Empirical mean based on MC
cat("Total à estimer :", val_x, "\nMoyenne des estimations obtenues :", mean(est_MC)) 
# should be close to 5e+08
# 500182431 e.g.
```

```{r}
# Variance estimation based on MC
cat("Theoretical variance:", varTHEO_x, "\nVariance associée aux échantillons de Monte Carlo :", var(est_MC))
# 8.512412e+13 e.g.
```

@@

  # 2nd step: creating the values corresponding to the function
  rho_MC <- tibble(.rows = n)
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
    colnames(rho_MC) <- col_names
  }
  colnames(rho_MC) <- col_names

@@

  return(c(mean(est_MC), var(est_MC)))
  # Estimated value and Monte-Carlo variance
}
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
cat("True integral:", 1e+06, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res[2])
# Totals: 1e+06 and 1e+06 (Equality as always)
# Variances: 0 and 0 (Equality as always)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
cat("True integral:", 500000, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res[2])
# Ex:
# True integral: 5e+05 
# Mean of all the estimations: 499214

# Theoretical variance: 2.5e+08 
# Monte-Carlo variance: 245287491
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
cat("True integral:", 5e+08, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res[2])
# Ex:
# True integral: 5e+08 
# Mean of all the estimations: 499874718

# Theoretical variance: 8.333333e+13 
# Monte-Carlo variance: 7.99389e+13
```

### 2024-07-08 Trees_no_grid.Rmd
No excluded tree

@@

  true_value <- nrow(trees) # Theoretical value
  est_value <- mean(est_MC) # Estimated value
  return(c(true_value, est_value))
}
```

```{r}
res <- true_vs_MC(n = 100, B = 1000, R = 5)
cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
# Ex:
# True number of trees: 30942 
# Mean of all the estimations (Monte Carlo): 30954.24
```

>>>>

```{r}
### Necessary step to calculate the theoretical variance

# Creating a local variable (cf pages 10-11 in Trinh et alii (2024))
local_var2 <- c()
source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
for (placette in 1:n) {
  local_var2 <- append(local_var2, (sum(trees_in[trees_in[placette] != 0,]/inc_area(c(random_points[placette,]$x, random_points[placette,]$y),0,0,1000,1000,R)))^2)
}

est_nb2 <- sum((local_var2)/p)

cat("An estimation of the total number of trees based on the sample:", )
```

@@

  return(c(nrow(trees), mean(est_MC), var(est_MC)))
  # Theoretical value of the total, estimated value of the total, Monte-Carlo variance
}
```

```{r}
res <- true_vs_MC(n = 100, B = 1000, R = 5)
cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
cat("\n\nTheoretical variance:", , "\nMonte-Carlo variance:", res[3])
# Ex:
# True number of trees: 30942 
# Mean of all the estimations (Monte Carlo): 30954.24
```
